### 2019-06-09 thesis-template/msc-thesis.tex
update

\documentclass[
     12pt,         % font size
     a4paper,      % paper format
     BCOR10mm,     % binding correction
     DIV14,        % stripe size for margin calculation
%     liststotoc,   % table listing in toc
%     bibtotoc,     % bibliography in toc
%     idxtotoc,     % index in toc
%     parskip       % paragraph skip instad of paragraph indent
     ]{scrreprt}

@@

\vspace{0.5\baselineskip}
{\huge
\textbf{Global Illumination Techniques for Tensor Field Visualization}
}
\end{center}

@@

\chapter*{Abstract}
%\input{abstract}
Tensor fields, are most commonly associated with stress distributions (cf. Cauchy-stress tensor) in 2D/3D grids, but also have some other meanings in practice in physics. By means of global illumination techniques, we motivate a new method to visualize tensor fields, which is also capable of visualizing the light transport (propagation) in a topologically defined scene geometry. As a basis, we derive a simple light propagation scheme for Cartesian grids, which satisfies propagation attenuation and energy-conservation principles and is able to approximate light distributions for given light source position(s) and direction(s) until convergence. The transmission profiles within this grid are considered as crystal fiber structures as an underlying physical model (eg. gemstones: tiger's eye's cat's eye effect). The consequent task is to model anisotropic fibre structures with the orientation and anisotropy measures of the underlying tensor field in the grid.
For this, we derive an eigenbasis by PCA (principal component analysis) for every cell of the tensor field and form an ellipsoid equation as transmission (transfer/weighting) function for the transmitted light profiles. Hence, the resulting light distribution can be visualized via 2D scalar field or polar plots for directional information. Additionally, We measure impulse responses of the tensor field with Dirac-pulses as light sources at any (sampled) position and in any direction to generate a uniform sampled map of the global illumination distributions. This map is considered as a global illumination energy flow field.
We gain inspiration by vector field particle tracing's FTLE approach for analyzing the gradient of the flow field of the resulting light distributions. Similar to how the FTLE detects ridges/LCS (Lagrangian coherent structures) in vector fields (flow fields), our approach captures these structures likewise, attracting/repelling/saddling tensor field lines (TFL) which frequently represent key structures in nature, in tensor fields. We denote this entity a global illumination gradient which states an FTLE-related approach for visualizing LCS in tensor fields through analysis of the global and light transport  directed by imprint/engraving in crystelline fiber structures modeled by the tensor field's ellipsoid glyhps. 
We also introduce Deformation Ellipsoid glyphs which are, additionally to visualizing anisotropic topology, pointing inward/outward for compressive/tensile stresses visualizing orientation of principal mechanical stresses.
We evaluate our approaches for plausibility and comparability within an extensive test campaign.
\newpage

@@

\paragraph{Contributions of this Work}
\begin{itemize}
	\item
\end{itemize}
%Dieses Kapitel gibt einen Überblick über die Arbeit. Gerade der
%Abschnitt zur Motivation soll allgemein verständlich geschrieben
%werden. Die Einleitung sollte auch wichtige Referenzen enthalten.

@@

Tensor Field Visualization is gaining importance as a relevant tool for the analysis of fluid and solid mechanics. Tensors are found most commonly in medical, scientific and engineering applications. A tensor is a $n$-D generalization of a matrix and appears, e.g., as Jacobian-Matrix in vector (Flow) field visualization or as stress tensor in solid continuum mechanics. Basically, tensors describe compressions, tensions, rotations and volume changes in both solid and fluid material. While most techniques focus on symmetric tensor field visualization (like glyphs and tensor field lines), some other recent works adress the problem of asymmetric tensor field visualization. The issue with asymmetric or antisymmetric tensors is that they do not always yield real eigenvalues, which is needed to determine an eigenbasis to set up glyphs, hyperstreamlines or tensor field lines. \cite{pang&zheng} et al. proposed the concept of dual eigenvectors and \cite{zhang} extended it to pseudo-eigenvectors and introduced eigenvector and eigenvalue manifold to visualize eigenvectors in the complex domain. In this work, we will use the $\mathbf{U}$-matrix obtained from singular value decomposition (SVD) to obtain the half-axes of the PCA principal ellipsoid as suggested by \cite{moler}.\\

@@

Principal Component Analysis is an algorithm which can capture the principal components (directions) in stochastic data. But it works similarly on transformations to capture the principal directions from transformations like rotation and scaling. Now, principal component analysis can be done by eigenvalue or singular vector decomposition, whereas the former yields complex eigenvalues for asymmetric matrices. For (skew-)symmetric (normal) matrices, they are connected through the following relation: $s_i = \sqrt{|\lambda_i|}$ (cf. \cite{kieburg}). Note that the eigenvectors match the singular vectors only for symmetric matrices, which does not mean that they do not form the half-axes of the principal component ellipsoid in other cases. Mathematically speaking, a decomposition is somehow decomposing a transformation (which follows certain transformation rules) into parts of subsequent transformations consistent of rotation and scaling ($\mathbf{A} = \mathbf{R}\mathbf{S}\mathbf{R}^*$). We choose to use singular value decomposition ($\mathbf{A} = \mathbf{U} \mathbf{\Sigma} \mathbf{V}^*$) to be able to set up real eigenvalues for any kind of matrix (singular values are always real and positive). Also, the singular vectors of the $\mathbf{U}$-matrix represent the half-axes of the principal ellipsoid (eigenframe) shown in Fig. \ref{HAT} for any kind of matrix as pointed out by \cite{moler}. In addition, we also calculate the eigenvalues to exploit the sign of the real part of the eigenvalues \cite{mroz} ordered decreasingly by absolute value (corresponding to singular value order). The sign corresponds to tensile ($+$) and compressive ($-$) stress, which would allow us to visualize deformation glyphs with arrows pointing inwards for compressive and outwards for tensile stresses. We do this decomposition analysis once for each matrix and then store the precomputed results in a grid. The principal ellipsoid is also used as a transmission profile for the propagation scheme in symbolic form in a subequent step. In this work, we will use the singular vectors yielded from singular value decomposition to avoid complex values yielded from eigenvalue decomposition. This will allow us to set up glyphs representing the major/minor axis of the underlying transformation for every kind of (asymmetric/symmetric) tensor. We will then use global-illumination techniques on top to generate a flow map, which permits us to compute an FTLE-like field on the tensor fields.

@@

\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/rings.png}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/tensorfieldlines.png}
    \label{b)}
  \end{minipage}
\caption{a) ``rings''-testfield, b) tensor field lines for a)}
\label{drain}
\end{figure}
\section{Related Work}
\label{sec:related}

@@

There has been extensive recent work on symmetric tensors but in comparison little on asymmetric ones. Since we aren't able to cover the whole scope in this work, we will focus on the most relevant works on tensor field visualization. We will talk about the publications from \cite{} and \cite{} in particular, since they pose thematically related works.\vskip 5pt

\textbf{Symmetric Tensor Field Visualization}\\
\cite{pang&zheng} et al. proposed a texture-based visualization approach called HyperLIC, which extends the concept of LIC to symmetric tensor fields by using an anisotropic 2D-filter kernel oriented along the major/minor eigenvectors. The concept of following the major/minor eigenvector along tensor field lines was invented by \cite{vilanova}. Tensorlines introduce a kind of artificial inertia (running average), making them resistent to noise. The notion of tensor field topology and the concept of Hyperstreamlines was first introduced by \cite{delmarcelle&hesselink}. The placement of tensor field lines as hyperstreamlines was recently improved by \cite{spencer} et al. for glyph packing. A good overview of seeding strategies concerning glyphs is given by \cite{mcloughlin}. \cite{feng} et. al. used Voronoi Tesselation for placing the glyphs. Superquadric glyphs have been proposed by \cite{schultz&kindlmann} for general (non-positive definite) tensors. \cite{deleeuw&vanwijk} visualize the partial derivative gradient, the Jacobian of the tensor field to sense the local properties of the field. A diffusion tensor can also be visualized by box \cite{makris}, ellipsoid \cite{pierpaoli}, composite \cite{worth} or superquadric \cite{kindlmann} glyphs. There is also a set of scalar measures available in symmetric tensor field visualization such as: mean diffusivity, fractional anisotropy \cite{basser} and anisotropy coefficients \cite{westin}. \cite{hlawatsch} et al. obtain a coordinate (flow) map from tensor field lines following major/minor eigenvectors (fibre trajectories) and use the maximum eigenvalue of the Cauchy-Green deformation tensor to compute the FTLE-field in homogeneous regions. In a similar manner, we opt to use Global Illumination Techniques to obtain a light distribution footprinted (in form of weighting profiles obtained from ellipsoid glyphs) by the tensor field.
\\
\textbf{Asymmetric Tensor Field Visualization}\\
\cite{pang&zheng} et al. proposed the concept of dual eigenvectors and \cite{zhang} extended it to pseudo-eigenvectors and introduced the eigenvector/eigenvalue manifolds to visualize eigenvectors in the complex domain. \cite{laramee} et al. focused on the efficient implementation and visualization of these structures and provided an interactive visualization system for asymmetric tensors applicable in fluid and solid dynamics. The concept of Tensor Magnitude has been introduced by \cite{laramee2} for means of physical interpretation. They also proposed an efficient glyph and hyperstreamline hybrid approach, which made dynamic interaction in real-time in 2D tensor fields feasible. \cite{palacios} extracted isosurfaces of tensor magnitude, mode and isotropy index. \vskip 5pt

The FTLE-related approach ``global illumination gradient'' to be designed states a generalization of the light transport visualization method FTPD proposed by \cite{zirr}, since it allows a similar measure to be computed through defining a geometrical scene and setting the transmission (tensor field) to an isotropic and constant value of $100\%$. In this modus, the approach operates as a light transport visualitation technique. The work of \cite{hlawatsch} et.al. obtains similar results (an FTLE-like field) but obtains them by sampling of fiber trajectories instead of global illumination light transport methods, as in our case.
%Typischerweise im letzten Abschnitt dieses Kapitels wird dann auf
%verwandte Arbeiten eingegangen. Entsprechende Arbeiten sind geeignet
%zu zitieren. Beispiel: Die wurde erstmalig in den Arbeiten von Spitz
%und Gertz \cite{Spitz2016a} gezeigt \ldots Details dazu werden in
%dem Buch von Newman zu Netzwerken \cite{Newman2010} erläutert \ldots.

@@

\section{Global Illumination (Propagation) Scheme}
\label{sec:scheme}
Within the scope of this work, we will motivate a Global Illumination Scheme designed to efficiently propagate the intensities stored in discrete polar coordinates given as impulses (stimuli) by the user or the config. Polar profiles for different light sources are shown in Fig. \ref{polar}:
\begin{figure}[!t]
  \centering
 {
    \includegraphics[width=0.8\textwidth]
    {img/strahler.png}
  }
  \caption{Polar profiles for different types of emitters ($m=0$: spherical emitter, $m=1$: Lambert emitter, $m=2$: cone emitter}
  \label{polar}
\end{figure}\vskip 3pt
As a reminder, polar profiles map each angle $\varphi$ a magnitude $r$ forming a function $r(\varphi)$. They are circular axis versions of the domain $[0..2\pi]$, with negative magnitudes mirrored by 180 degrees). Thus, they are functions with an angular domain making them directionally dependent, which is a well suited representation for point lights, as we use them in a style of \cite{dachsbacher} et al. For the sake of interpretability, we exclude negative values (energies) from the scope of our calculations. As a start-up thinker for the propagation scheme, we will think of a grid cell in 2D as a center pixel within an 8-neighborhood. Remember, that all considerations from now on are given concerning a single grid cell respectively. It has 8 (4 faces/edges and 4 diagonals) unique neighbors, which are adjacent point lights in the grid (the type of light source with theoretically no finite extend). We consider one face neighbor (top) to shortly explain the steps of the scheme. The diagonals and the others are obtained from derivation and symmetry.

@@

We place a cosine lobe scaled with the integrated (accumulated) energies in each of the 8 cone directions, whereas outgoing integrated and summed energies are weighted by the linear combination weights (factors) in overlapping (green) areas to split up the contributions accordingly. The contribution areas are depicted in Fig. \ref{scheme}, the cosine lobes can be observed in Fig. \ref{iter} respectively. This manner of propagation is inspired by the propagation scheme of \cite{dachsbacher} et al. (see the paper on how to ``project the flux into a point light''). The implementation is done in a dual buffer approach which pushes the energies back and forth (buffer A to buffer B) until convergence, which happens when the energy is spreaded throughout the grid and enters a stationary state, characterized by equal out (at grid borders) to in (at light source positions) energy-flow with no more nettings going on inside the domain. We measure the convergence criterion by setting up an overall distribution error w.r.t to the previous iteration. Note that even though we propagate the energy directly through the diagonal cones (which forms a square initially), the 8 degrees of freedom introduce a circular (spherical) wave front after few iterations (for greater resolutions) as depicted in Fig. \ref{iter}. This occurs, since the diagonals are more strongly attenuated by default and there is a redistribution of intensities in the long term resulting in a circular torus-shaped distribution, as observed in Fig. \ref{iter}. Also note, that this approach satisfies energy conservation and propagation attenuation principles and applies to the principles of light propagation in vacuum (by default). The verification of these principal requirements and specifications can be observed in the Experimental Evaluation in chap. \ref{chap:eval}.

@@

\bibliographystyle{apalike}
% b) The File:
\bibliography{references}

>>>>

\documentclass[enabledeprecatedfontcommands,
     12pt,         % font size
     a4paper,      % paper format
     BCOR10mm,     % binding correction
     DIV14,        % stripe size for margin calculation
%     liststotoc,   % table listing in toc
%     bibtotoc,     % bibliography in toc
%     idxtotoc,     % index in toc
%     parskip       % paragraph skip instad of paragraph indent
     ]{scrreprt}

@@

\vspace{0.5\baselineskip}
{\huge
\textbf{Light Transport Techniques for Tensor Field Visualization}
}
\end{center}

@@

\chapter*{Abstract}
%\input{abstract}
Tensor fields, are most commonly associated with stress distributions (cf. Cauchy-stress tensor) in 2D/3D grids, but also have some other meanings in practice in physics. By means of global illumination techniques, we motivate a new method to visualize tensor fields, which is also capable of visualizing the light transport (propagation) in a topologically defined scene geometry. As a basis, we derive a simple light propagation scheme for Cartesian grids, which satisfies propagation attenuation and energy-conservation principles and is able to approximate light distributions for given light source position(s) and direction(s) until convergence. The transmission profiles within this grid are considered as crystal fiber structures as an underlying physical model (eg. gemstones: tiger's eye's cat's eye effect). The consequent task is to model anisotropic fibre structures with the orientation and anisotropy measures of the underlying tensor field in the grid.
For this, we derive an eigenbasis by PCA (principal component analysis) for every cell of the tensor field and form an ellipsoid equation as transmission (transfer/weighting) function for the transmitted light profiles. Hence, the resulting light distribution can be visualized via 2D scalar field or polar plots for directional information. Additionally, We measure impulse responses of the tensor field with Dirac-pulses as light sources at any (sampled) position and in any direction to generate a uniform sampled map of the global illumination distributions. This map is considered as a global illumination energy flow field.
We gain inspiration by vector field particle tracing's FTLE approach for analyzing the gradient of the flow field of the resulting light distributions. Similar to how the FTLE detects ridges/LCS (Lagrangian coherent structures) in vector fields (flow fields), our approach captures these structures likewise, attracting/repelling/saddling tensor field lines (TFL) which frequently represent key structures in nature, in tensor fields. We denote this entity a global illumination gradient which states an FTLE-related approach for visualizing LCS in tensor fields through analysis of the global and light transport  directed by imprint/engraving in crystelline fiber structures modeled by the tensor field's ellipsoid glyhps. We evaluate our approaches for plausibility and comparability within an extensive test campaign and demonstrate its performance on several examples of datasets.
\newpage

@@

\paragraph{Contributions of this Work}
\begin{itemize}
	\item Motivation of a light transport technique following basic but crucial physical principles for tensor field visualization
	\item Design of a FTLE-related approach for visualizing key structures (ROIs) in $2D$ second-order tensor fields
	\item Discussion of the proposed techniques in the context of other works in this field
\end{itemize}
%Dieses Kapitel gibt einen Überblick über die Arbeit. Gerade der
%Abschnitt zur Motivation soll allgemein verständlich geschrieben
%werden. Die Einleitung sollte auch wichtige Referenzen enthalten.

@@

Tensor Field Visualization is gaining importance as a relevant tool for the analysis of fluid and solid mechanics. Tensors are found most commonly in medical, scientific and engineering applications. A tensor is a $n$-D generalization of a matrix and appears, e.g., as Jacobian-Matrix in vector (Flow) field visualization or as stress tensor in solid continuum mechanics. Basically, tensors describe compressions, tensions, rotations and volume changes in both solid and fluid material. While most techniques focus on symmetric tensor field visualization (like glyphs and tensor field lines), some other recent works adress the problem of asymmetric tensor field visualization. The issue with asymmetric or antisymmetric tensors is that they do not always yield real eigenvalues, which is needed to determine an eigenbasis to set up glyphs, hyperstreamlines or tensor field lines. \cite{pang&zheng} Zheng \& Phang et al. proposed the concept of dual eigenvectors and \cite{zhang} Lin et al. extended it to pseudo-eigenvectors and introduced eigenvector and eigenvalue manifold to visualize eigenvectors in the complex domain. In this work, we will use the $\mathbf{U}$-matrix obtained from singular value decomposition (SVD) to obtain the half-axes of the PCA principal ellipsoid as suggested by Moler \cite{moler}.\\

@@

Principal Component Analysis is an algorithm which can capture the principal components (directions) in stochastic data. But it works similarly on transformations to capture the principal directions from transformations like rotation and scaling. Now, principal component analysis can be done by eigenvalue or singular vector decomposition, whereas the former yields complex eigenvalues for asymmetric matrices. For (skew-)symmetric (normal) matrices, they are connected through the following relation: $s_i = \sqrt{|\lambda_i|}$ (cf. \cite{kieburg}). Note that the eigenvectors match the singular vectors only for symmetric matrices, which does not mean that they do not form the half-axes of the principal component ellipsoid in other cases. Mathematically speaking, a decomposition is somehow decomposing a transformation (which follows certain transformation rules) into parts of subsequent transformations consistent of rotation and scaling ($\mathbf{A} = \mathbf{R}\mathbf{S}\mathbf{R}^*$). We choose to use singular value decomposition ($\mathbf{A} = \mathbf{U} \mathbf{\Sigma} \mathbf{V}^*$) to be able to set up real eigenvalues for any kind of matrix (singular values are always real and positive). Also, the singular vectors of the $\mathbf{U}$-matrix represent the half-axes of the principal ellipsoid (eigenframe) shown in Fig. \ref{HAT} for any kind of matrix as pointed out by Moler \cite{moler}. In addition, we also calculate the eigenvalues to exploit the sign of the real part of the eigenvalues (\cite{mroz}) ordered decreasingly by absolute value (corresponding to singular value order). The sign corresponds to tensile ($+$) and compressive ($-$) stress, which would allow us to visualize deformation glyphs with arrows pointing inwards for compressive and outwards for tensile stresses. We do this decomposition analysis once for each matrix and then store the precomputed results in a grid. The principal ellipsoid is also used as a transmission profile for the propagation scheme in symbolic form in a subequent step. In this work, we will use the singular vectors yielded from singular value decomposition to avoid complex values yielded from eigenvalue decomposition. This will allow us to set up glyphs representing the major/minor axis of the underlying transformation for every kind of (asymmetric/symmetric) tensor. We will then use global-illumination techniques on top to generate a flow map, which permits us to compute an FTLE-like field on the tensor fields.

@@

\begin{figure}[!t]
\centering
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/rings.png}
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/tensorfieldlines.png}
    \label{b)}
  \end{minipage}
\caption{a) ``rings''-testfield, b) tensor field lines for a)}
\label{drain}
\end{figure}

@@

\section{Related Work}
\label{sec:related}

There has been extensive recent work on symmetric tensors but in comparison little on asymmetric ones. Since we aren't able to cover the whole scope in this work, we will focus on the most relevant works on tensor field visualization. We will talk about the publications from Hlawatsch et al. \cite{hlawatsch} and Zirr et al. \cite{zirr} in particular, since they pose thematically related works.\vskip 5pt

\textbf{Symmetric Tensor Field Visualization}\\
Zheng \& and Pang \cite{pang&zheng} et al. proposed a texture-based visualization approach called HyperLIC, which extends the concept of LIC to symmetric tensor fields by using an anisotropic 2D-filter kernel oriented along the major/minor eigenvectors. The concept of following the major/minor eigenvector along tensor field lines was invented by Vilanova et al. \cite{vilanova}. Tensorlines introduce a kind of artificial inertia (running average), making them resistent to noise. The notion of tensor field topology and the concept of Hyperstreamlines was first introduced by Delmarcelle and Hesselink \cite{delmarcelle&hesselink}. The placement of tensor field lines as hyperstreamlines was recently improved by Spencer et al. \cite{spencer} for glyph packing. A good overview of seeding strategies concerning glyphs is given by McLoughlin et al. \cite{mcloughlin}. Feng et al. \cite{feng} used Voronoi Tesselation for placing the glyphs. Superquadric glyphs have been proposed by Schultz and Kindlmann \cite{schultz&kindlmann} for general (non-positive definite) tensors. De Leeuw and Van Wijk \cite{deleeuw&vanwijk} visualize the partial derivative gradient, the Jacobian of the tensor field to sense the local properties of the field. A diffusion tensor can also be visualized by box \cite{makris}, ellipsoid \cite{pierpaoli}, composite \cite{westin2} or superquadric \cite{kindlmann} glyphs. There is also a set of scalar measures available in symmetric tensor field visualization such as: mean diffusivity, fractional anisotropy \cite{basser} and anisotropy coefficients \cite{westin}. Hlawatsch et al. \cite{hlawatsch} obtain a coordinate (flow) map from tensor field lines following major/minor eigenvectors (fibre trajectories) and use the maximum eigenvalue of the Cauchy-Green deformation tensor to compute the FTLE-field in homogeneous regions. In a similar manner, we aim to use light transport techniques to obtain a final light distribution through successive light propagation cycles footprinted (in form of transmission profiles obtained from ellipsoid glyphs) by the tensor field.
\\
\textbf{Asymmetric Tensor Field Visualization}\\
Zheng and Pang \cite{pang&zheng} proposed the concept of dual eigenvectors and Zhang et al. \cite{zhang} extended it to pseudo-eigenvectors and introduced the eigenvector/eigenvalue manifolds to visualize eigenvectors in the complex domain. Laramee et al. \cite{laramee} focused on the efficient implementation and visualization of these structures and provided an interactive visualization system for asymmetric tensors applicable in fluid and solid dynamics. The concept of Tensor Magnitude has been introduced by \cite{laramee2} for means of physical interpretation. They also proposed an efficient glyph and hyperstreamline hybrid approach, which made dynamic interaction in real-time in 2D tensor fields feasible. Palacios et al. \cite{palacios} extracted isosurfaces of tensor magnitude, mode and isotropy index. \vskip 5pt

Last, we will discuss our approach in relation to the listed publications. The FTLE-related approach ``global illumination gradient'' to be designed states a generalization of the light transport visualization method FTPD proposed by Zirr et al.\cite{zirr}, since it allows a similar measure to be computed through defining a geometrical scene and setting the transmission (tensor field) to an isotropic and constant value of $100\%$. In this modus, the approach operates as a light transport visualitation technique. The work of \cite{hlawatsch} et al. obtains similar results (an FTLE-like field) but obtains them by sampling of fiber trajectories instead of global illumination light transport methods, as in our case.
%Typischerweise im letzten Abschnitt dieses Kapitels wird dann auf
%verwandte Arbeiten eingegangen. Entsprechende Arbeiten sind geeignet
%zu zitieren. Beispiel: Die wurde erstmalig in den Arbeiten von Spitz
%und Gertz \cite{Spitz2016a} gezeigt \ldots Details dazu werden in
%dem Buch von Newman zu Netzwerken \cite{Newman2010} erläutert \ldots.

@@

\section{Global Illumination (Propagation) Scheme}
\label{sec:scheme}
Within the scope of this work, we will motivate a Global Illumination Scheme designed to efficiently propagate the intensities stored in discrete polar coordinates given as impulses (stimuli) by the user or the config. Polar profiles for different light sources are shown in Fig. \ref{polar}:
\begin{figure}[!t]
  \centering
 {
    \includegraphics[width=0.8\textwidth]
    {img/strahler.png}
  }
  \caption{Polar profiles for different types of emitters ($m=0$: spherical emitter, $m=1$: Lambert emitter, $m=2$: cone emitter}
  \label{polar}
\end{figure}\vskip 3pt
As a reminder, polar profiles map each angle $\varphi$ a magnitude $r$ forming a function $r(\varphi)$. They are circular axis versions of the domain $[0..2\pi]$, with negative magnitudes mirrored by 180 degrees). Thus, they are functions with an angular domain making them directionally dependent, which is a well suited representation for point lights, as we use them in a style of Dachsbacher et al. \cite{dachsbacher}. For the sake of interpretability, we exclude negative values (energies) from the scope of our calculations. As a start-up thinker for the propagation scheme, we will think of a grid cell in 2D as a center pixel within an 8-neighborhood. Remember, that all considerations from now on are given concerning a single grid cell respectively. It has 8 (4 faces/edges and 4 diagonals) unique neighbors, which are adjacent point lights in the grid (the type of light source with theoretically no finite extend). We consider one face neighbor (top) to shortly explain the steps of the scheme. The diagonals and the others are obtained from derivation and symmetry.

@@

We place a cosine lobe scaled with the integrated (accumulated) energies in each of the 8 cone directions, whereas outgoing integrated and summed energies are weighted by the linear combination weights (factors) in overlapping (green) areas to split up the contributions accordingly. The contribution areas are depicted in Fig. \ref{scheme}, the cosine lobes can be observed in Fig. \ref{iter} respectively. This manner of propagation is inspired by the propagation scheme of Dachsbacher et al. \cite{dachsbacher} (see the paper on how to ``project the flux into a point light''). The implementation is done in a dual buffer approach which pushes the energies back and forth (buffer A to buffer B) until convergence, which happens when the energy is spreaded throughout the grid and enters a stationary state, characterized by equal out (at grid borders) to in (at light source positions) energy-flow with no more nettings going on inside the domain. We measure the convergence criterion by setting up an overall distribution error w.r.t to the previous iteration. Note that even though we propagate the energy directly through the diagonal cones (which forms a square initially), the 8 degrees of freedom introduce a circular (spherical) wave front after few iterations (for greater resolutions) as depicted in Fig. \ref{iter}. This occurs, since the diagonals are more strongly attenuated by default and there is a redistribution of intensities in the long term resulting in a circular torus-shaped distribution, as observed in Fig. \ref{iter}. Also note, that this approach satisfies energy conservation and propagation attenuation principles and applies to the principles of light propagation in vacuum (by default). The verification of these principal requirements and specifications can be observed in the Experimental Evaluation in chap. \ref{chap:eval}.

@@

\bibliographystyle{ieeetr} %acm - as capital letter ALTERNATIVE
% b) The File:
\bibliography{references}
